---
title: "Measurement and Characterization of a 5T Solenoid Field"
output: html_notebook
---

##Abstract

This project involved analyzing the magnetic field generated by the 5T Solenoid magnet in the CLAS12 detector.  This is done to understand the variances from specifications of the magnetic field due to manufacturing and/or installation defects.

#CLAS12 - 


```{r Init, include=FALSE}
options(java.parameters = "-Xmx8000m")
library(googlesheets)
library(dplyr)
library(ggplot2)
library(plotly)
library(akima)
suppressMessages(library(dplyr))
source("functions.R")
library(xlsx)
library(stats)
library(varhandle)
library(webshot)
```

The Model

```{r}
r0BzVx
```
```{r, echo=FALSE}
plot(mind[c("theta", "CenterZ", "FittedCenterZ")])
```


The Data

```{r}

```



Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

```{r, echo=FALSE}
r0BzVx
r0BxVz
r0ByVz

r1BzVz
r1BxVz
r1ByVz
r1BxBzVz
r1ByVz

r30BzVz
r30BxVz
r30ByVz
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
