---
title: "R Notebook"
output: html_notebook
---
```{r Init, include=FALSE}
options(java.parameters = "-Xmx8000m")
library(googlesheets)
library(dplyr)
library(ggplot2)
library(plotly)
library(akima)
suppressMessages(library(dplyr))
source("functions.R")
library(xlsx)
library(stats)
library(varhandle)
library(webshot)
```

The Model

```{r}
plot(mind[c("Run", "CenterZ", "FittedCenterZ")])
```
```{r}
plot(mind[c("theta", "CenterZ", "FittedCenterZ")])
```


The Data

```{r}

```



Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

```{r}
r0BzVx
r0BxVz
r0ByVz

r1BzVz
r1BxVz
r1ByVz
r1BxBzVz
r1ByVz

r30BzVz
r30BxVz
r30ByVz
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
